---
title: "p8105_hw1_xc2473"
output: github_document
---
Problem One:
```{r}
library(tidyverse)

ran_sample = rnorm(8)
vec_logic = ifelse(ran_sample > 0, TRUE, FALSE)
vec_char = c("A", "B", "C", "D", "E", "F", "G", "H")
vec_factor = factor(c("low", "low", "medium", "medium", "high", "high", "low", "high"))

question_1_df = tibble(
  ran_sample,
  vec_logic,
  vec_char,
  vec_factor
)

mean(ran_sample)
mean(vec_logic)
mean(vec_char)
mean(vec_factor)
```
We only succeed in taking the mean of ran_sample which is numeric and vec_logic which is logical vector. It doesn't work for character and factor vector to take means.

```{r echo = TRUE, results= "hide"}
as.numeric(vec_logic)
as.numeric(vec_char)
as.numeric(vec_factor)
```
It is found that logical and factor vector could be converted into numeric value, while the character vector could not. It can explain why logical vetor can take the mean.

```{r}
A = as.numeric(vec_logic) * ran_sample
B = as.factor(vec_logic) * ran_sample
C = as.numeric(as.factor(vec_logic)) * ran_sample
```
Error occur when we run the second-row code in the code chunk above, since the factor vector cannot multiply other variables.

Problem Two:
```{r}
x = rnorm(500)
y = rnorm(500)
vec_logic_1 = ifelse((x + y) > 1, TRUE, FALSE)
num = as.numeric(vec_logic_1)
fac = as.factor(vec_logic_1)

question_2_df = tibble(
  x,
  y,
  vec_logic_1,
  num,
  fac
)
```
This dataset contain `r nrow(question_2_df)` rows and `r ncol(question_2_df)` columns.
The mean of x is `r mean(x)`.
The median of x is `r median(x)`.
The standard deviation of x is `r sd(x)`.
The proportion of cases for which x + y > 1 is `r sum(vec_logic_1, na.rm = TRUE)/nrow(question_2_df)`.

```{r}
ggplot(question_2_df, aes(x = x, y = y, color = "red")) + geom_point()

ggsave("myplot.pdf")

ggplot(question_2_df, aes(x = x, y = y, color = num)) + geom_point()
       
ggplot(question_2_df, aes(x = x, y = y, color = fac)) + geom_point()

```
